---
title: "CH5_QR_RMD"
author: "Fasih Atif"
date: "10/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Introduction to Analysis

I downloaded the GDP per capita and CO2 emissions per capita data from World Bank Indicators website. I took values of 2016 since there was no info on CO2 emissions per capita beyond 2016. I imported both tables and merged them together. There were a total of 264 countries(observations). I then filtered for missing values which left me with 238 observations.I then arranged the data in ascending order of gdp and split the data into 2 groups with the help of the median. All the countries with GDP per capita above and equal 5555.335 were assigned group 2 while the rest were assigned group 1. 

h0: There is no difference in average CO2 emissions per capita between the two groups

ha: There is a difference in average the CO2 emissions per capita between the the two groups

```{r, message = FALSE, warning=FALSE, include = FALSE}
data_in <- "C:/Users/abc/OneDrive/Business_Analytics/DA1-BA/Data_Analysis_1_Data_Exercise/atif-fasih_da1_data-exercise/CH5 Q5 (2 star)/"
co2_per_capita <- read_csv(paste0(data_in,"CO2_per_capita.csv"))

data_in <- "C:/Users/abc/OneDrive/Business_Analytics/DA1-BA/Data_Analysis_1_Data_Exercise/atif-fasih_da1_data-exercise/CH5 Q5 (2 star)/"
gdp_per_capita <- read_csv(paste0(data_in,"GDP_per_capita.csv"))
```

```{r, include = FALSE}
# Rename columns
co2_per_capita <- rename(co2_per_capita, 'country' = 'Country Name' ,'co2' = '2016')
gdp_per_capita <- rename(gdp_per_capita, 'country' = 'Country Name' , 'gdp' = '2016')
```

```{r, include = FALSE}
# Merge the two tables
gdp_co2_data <- merge(gdp_per_capita,co2_per_capita, by = 'country')
```

```{r,include = FALSE}
# Sort table by GDP
gdp_co2_data <- gdp_co2_data %>% arrange(gdp)
```

```{r,include = FALSE}
# Remove countries missing values
gdp_co2_data <- gdp_co2_data[complete.cases(gdp_co2_data),]
```

```{r,include = FALSE}
# Calculate median for splitting into 2 groups
median(gdp_co2_data$gdp)
```

```{r,include = FALSE}
# Split into 2 groups 
gdp_co2_data <- gdp_co2_data %>%
mutate('group' = ifelse(gdp >= 5555.335, 'group2','group1'))
```

Here is what the data looked like:
```{r}
head(gdp_co2_data,3)
tail(gdp_co2_data,3)
```
```{r,include = FALSE}
# No of observations in each group
table(gdp_co2_data$group)

```

I  then calculated the means of each group
```{r,message = FALSE, warning=FALSE}
group1_mean <- mean(gdp_co2_data$co2[gdp_co2_data$group == 'group1'])
group2_mean <- mean(gdp_co2_data$co2[gdp_co2_data$group == 'group2'])
```

I calculated the difference in observed mean of the 2 groups

```{r,message = FALSE, warning=FALSE}
mean_diff <- group2_mean - group1_mean
```

I proceeded to create the Bootstrap procedure with 10000 samples
```{r,message = FALSE, warning=FALSE}
set.seed(13456)
n_group1 <- 119
n_group2 <- 119

# No of boostrap samples
B <- 10000
```

I converted the Boot-sample into a column
```{r,message = FALSE, warning=FALSE}

boot_group1 <- matrix(sample(gdp_co2_data$co2[gdp_co2_data$group == 'group1'],
size = B*n_group1, replace = TRUE),ncol = B,nrow = n_group1)

boot_group2 <- matrix(sample(gdp_co2_data$co2[gdp_co2_data$group == 'group2'],
size = B*n_group2, replace = TRUE),ncol = B, nrow = n_group2)

```

I calculated the difference in MEANS for each of the bootsamples
```{r,message = FALSE, warning=FALSE}
Boot_diff_in_means <- colMeans(boot_group1) - colMeans(boot_group2)
```

The "PERCENTILE" bootstrap confidence interval (95%)
```{r,message = FALSE, warning=FALSE}
quantile(Boot_diff_in_means, prob = 0.025)
quantile(Boot_diff_in_means, prob = 0.975)
```

The standard Error
```{r}
std <- sd(gdp_co2_data$co2)
SE <- std/238^1/2
SE

```
### Result
We are 95% confident that the true/population difference in means of CO2 emissions per capita between the two groups is somewhere between -7.27 and -4.93. We reject null hypothesis.